\documentclass[a4paper,12pt,oneside,fleqn]{article}
\usepackage[latin1]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[finnish, english]{babel}
\usepackage{times}
\usepackage[pdftex]{graphicx}
\usepackage[left=35mm,right=20mm,top=20mm,bottom=25mm]{geometry}
\usepackage{setspace}
\usepackage{sectsty}
\usepackage{fancyhdr}
\usepackage{icomma}
\usepackage{amssymb,amsmath}
\usepackage[titles]{tocloft}
\usepackage{ccaption}
\usepackage{natbib}
\usepackage{colortbl}
\usepackage[none]{hyphenat}
\sloppy

\graphicspath{{figures/}}

\setlength{\headheight}{10mm}
\pagestyle{fancy}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\singlespacing
\newenvironment{equation_text}[0]
{\begin{list}{}{\setlength{\leftmargin}{25mm}}}
{\end{list}}

\newcommand{\researchname}[0]{Project proposal}

\newcommand{\flabel}[1]{\label{fig:#1}}
\newcommand{\tlabel}[1]{\label{tab:#1}}
\newcommand{\elabel}[1]{\label{eq:#1}}
\newcommand{\slabel}[1]{\label{sec:#1}}

\newcommand{\fref}[1]{Figure~\ref{fig:#1}}
\newcommand{\tref}[1]{Table~\ref{tab:#1}}
\newcommand{\eref}[1]{Equation~\ref{eq:#1}}
\newcommand{\sref}[1]{Section~\ref{sec:#1}}

\newcommand{\tcaption}[1]{\caption{#1}\vspace{3mm}}

\newenvironment{enu}
{\begin{enumerate}
	\setlength{\topsep}{0pt}
  \setlength{\itemsep}{0pt}
  \setlength{\partopsep}{0pt}
  \setlength{\parskip}{0pt}
  \setlength{\parsep}{0pt}}
{\end{enumerate}}

\newenvironment{ite}
{\begin{itemize}
	\setlength{\topsep}{0pt}
  \setlength{\itemsep}{0pt}
  \setlength{\partopsep}{0pt}
  \setlength{\parskip}{0pt}
  \setlength{\parsep}{0pt}}
{\end{itemize}}

\renewcommand{\cftsecfont}{\normalfont}
\renewcommand{\cftsecpagefont}{\normalfont}
\renewcommand{\cftsecleader}{\cftdotfill{\cftdotsep}}
\setcounter{tocdepth}{3}
\setlength{\parskip}{0mm}
\setlength{\parindent}{0mm}
\setlength{\mathindent}{15mm}

\sectionfont{\fontfamily{phv}\fontseries{b}\fontsize{16pt}{18pt}\selectfont\uppercase}
\subsectionfont{\fontfamily{phv}\fontseries{b}\fontsize{14pt}{16pt}\selectfont}
\subsubsectionfont{\fontfamily{phv}\fontseries{m}\fontsize{12pt}{16pt}\selectfont}

\captiondelim{. }
\captionstyle{\raggedright}
\precaption{\hspace{5mm}}
\captiontitlefont{\fontfamily{phv}\fontshape{it}\fontsize{11pt}{12pt}\selectfont}
\bibpunct{/}{/}{,}{n}{}{,}

\definecolor{lightgrey}{rgb}{.8,.8,.8}
\definecolor{lightlightgrey}{rgb}{.9,.9,.9}
\definecolor{darkgrey}{rgb}{.5,.5,.5}
\definecolor{darkdarkgrey}{rgb}{.4,.4,.4}

\begin{document}

\renewcommand{\figurename}{\fontfamily{phv}\fontseries{b}\fontsize{11pt}{12pt}\selectfont Figure}
\renewcommand{\tablename}{\fontfamily{phv}\fontseries{b}\fontsize{11pt}{12pt}\selectfont Table}

% TITLE PAGE
\thispagestyle{empty}
\addtolength{\hoffset}{-5mm}
\begin{flushleft}
{\fontfamily{phv}\selectfont\textbf{EINDHOVEN UNIVERSITY OF TECHNOLOGY}} \\
{\fontfamily{phv}\selectfont\textbf{Department of Mathematics and Computer Science}} \\
{\fontfamily{phv}\selectfont\textbf{Department of Computer Science}} \\
{\fontfamily{phv}\selectfont\textbf{2II25 Web Technology}} \\
{\fontfamily{phv}\selectfont\textbf{Project part 2}} \\
\end{flushleft}

\vfill

\begin{center}
{\fontfamily{phv}\selectfont\textbf{\researchname}} \\
%{\fontfamily{phv}\selectfont Supervisor: Title Supervisor name} \\
\end{center}

\vfill

\begin{flushright}
\begin{tabular}{l}
{\fontfamily{phv}\selectfont In Eindhoven} \\
{\fontfamily{phv}\selectfont 30.03.2010} \\
{\fontfamily{phv}\selectfont Puputti Kimmo, Mórocz Ádám} \\
%{\fontfamily{phv}\selectfont student number} \\
{\fontfamily{phv}\selectfont k.p.puputti@student.tue.nl, morocz@gmail.com}
\end{tabular}
\end{flushright}
\clearpage

% SECTIONS
\pagestyle{fancy}
\fancyhf{}
\rhead{\thepage}
\setcounter{page}{1}
\setstretch{1.1}

\section{Motivation}

Everything that people do is somehow related to geographical
information. This is why a lot of the resources in WWW contain
geographical information. Place names, however, can be very ambiguous
and it can be hard to distinguish places from text
content. Geographical data is very linked within itself and
geographically annotated data can be easily linked together.\\

Our application lets you browse geographical data that is linked
within itself and also to other third party sites like Wikipedia
etc. We use the data from Geonames (http://www.geonames.org/) for
places inside The Netherlands in the backend of our application.\\

You can search for places by their name and browse through the pages
of each place. Every place is linked to several other places. You can
also see the places on a interactive map.

\section{Tools}

We use the required CherryPy Python web application framework for the
website, with Mako templates for the front end.\\

The backend itself runs on rdflib (http://www.rdflib.net/), which is
an RDF library for Python. We chose it because it seems to be the most
popular and matured RDF library for Python. There are also a number of
different data store solution for rdflib. We plan to first use SQLite
that is bundled with Python, but if it doesn't scale enough, we're
going to change to MySQL.\\

For the front end, we plan to use jQuery (http://jquery.org/)
JavaScript library and the Google Maps API for the interactive map
that can be moved and zoomed around.

\section{Use of Data}

Geographical data differs from country to country and it changes all
the time. Therefore, a fixed schema is not flexible enough to describe
the data.\\

RDF is a very flexible and general format. It is very well suited for
our application and it handles the varying and changing data
schema. We can also infer new information that is not explicitly in
the data, like getting the nearby places that are not linked in the
data by querying the child places under the parent place of the
current place.

\end{document}
